---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = 'center',
  fig.path = "man/figures/README-",
  dev = "png",
  fig.retina = 2,
  message = FALSE,
  warning = FALSE,
  tidy = FALSE
)
```

[![R build status](https://github.com/ncss-tech/sharpshootR/workflows/R-CMD-check/badge.svg)](https://github.com/ncss-tech/sharpshootR/actions)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/sharpshootR)](http://cran.r-project.org/web/packages/sharpshootR)
[![Total_Downloads](http://cranlogs.r-pkg.org/badges/grand-total/sharpshootR)](https://cran.r-project.org/package=sharpshootR)
[![sharpshootR Manual](https://img.shields.io/badge/docs-HTML-informational)](http://ncss-tech.github.io/sharpshootR/)

# sharpshootR

This package contains a mish-mash of functionality and sample data related to the daily business of soil survey operations with the USDA-NRCS. Many of the functions are highly specialized and inherit default arguments from the names used by the various NCSS (National Cooperative Soil Survey) databases.

## Installation

Get the stable version from CRAN:

```{r eval = FALSE}
install.packages('sharpshootR', dep = TRUE)
```

Get the development version from Github, after installing the CRAN version + dependencies:

```{r eval = FALSE}
remotes::install_github("ncss-tech/sharpshootR", dependencies=FALSE, upgrade=FALSE, build=FALSE)
```

### Install Suggested Packages
```{r eval = FALSE}
p <- c("MASS", "spdep", "circlize", "rvest", "xml2", "terra", 
       "raster", "exactextractr", "httr", "jsonlite", "igraph", 
       "dendextend", "testthat", "hydromad", "latticeExtra", 
       "farver", "venn", "gower", "daymetr", "elevatr", 
       "Evapotranspiration", "zoo", "SoilTaxonomy", "sf", "Hmisc"
)

install.packages(p)
```

## Website
[http://ncss-tech.github.io/AQP/](http://ncss-tech.github.io/AQP/)

## Examples

```{r fig.width=9, fig.height=5}
library(sharpshootR)
library(aqp)

# some example soil series, from soilDB::fetchOSD()
data("OSDexamples")

# extract Soil Profile Collection
x <- OSDexamples$SPC

# use the first 10 profiles
x <- x[1:10, ]

# arrange according to subgroup classification
SoilTaxonomyDendrogram(
  x, 
  KST.order = TRUE,
  scaling.factor = 0.02,
  cex.taxon.labels = 0.75,
  width = 0.33, 
  max.depth = 150, 
  depth.axis = list(line = -3, cex = 0.8, style = 'compact'),
  hz.distinctness.offset = 'hzd'
  )
```



## Citation
```{r}
citation("sharpshootR")
```

## Quick Reference

### Visualization
   * [`aggregateColorPlot`](http://ncss-tech.github.io/sharpshootR/reference/aggregateColorPlot.html)
   * [`aspect.plot`](http://ncss-tech.github.io/sharpshootR/reference/aspect.plot.html)
   * [`diagnosticPropertyPlot`](http://ncss-tech.github.io/sharpshootR/reference/diagnosticPropertyPlot.html)
   * [`plotAvailWater`](http://ncss-tech.github.io/sharpshootR/reference/plotAvailWater.html)
   * [`plotProfileDendrogram`](http://ncss-tech.github.io/sharpshootR/reference/plotProfileDendrogram.html)
   * [`plotSoilRelationGraph`](http://ncss-tech.github.io/sharpshootR/reference/plotSoilRelationGraph.html)
   * [`plotSoilRelationChordGraph`](http://ncss-tech.github.io/sharpshootR/reference/plotSoilRelationChordGraph.html)
   * [`plotTransect`](http://ncss-tech.github.io/sharpshootR/reference/plotTransect.html)
   * [`SoilTaxonomyDendrogram`](http://ncss-tech.github.io/sharpshootR/reference/SoilTaxonomyDendrogram.html)
   * [`vizGeomorphicComponent`](http://ncss-tech.github.io/sharpshootR/reference/vizHillslopePosition.html)
   * [`vizHillslopePosition`](http://ncss-tech.github.io/sharpshootR/reference/vizHillslopePosition.html)
   * [`vizFlatsPosition`](http://ncss-tech.github.io/sharpshootR/reference/vizFlatsPosition.html)
   * [`vizTerracePosition`](http://ncss-tech.github.io/sharpshootR/reference/vizTerracePosition.html)
   * [`vizMountainPosition`](http://ncss-tech.github.io/sharpshootR/reference/vizMountainPosition.html)
   * [`vizAnnualClimate`](http://ncss-tech.github.io/sharpshootR/reference/vizAnnualClimate.html)
   * [`plotWB`](http://ncss-tech.github.io/sharpshootR/reference/plotWB.html)
   * [`plotWB_lines`](http://ncss-tech.github.io/sharpshootR/reference/plotWB_lines.html)

   
### Climate
   * [`monthlyWB`](http://ncss-tech.github.io/sharpshootR/reference/monthlyWB.html)
   * [`simpleWB`](http://ncss-tech.github.io/sharpshootR/reference/simpleWB.html)
   * [`dailyWB`](http://ncss-tech.github.io/sharpshootR/reference/dailyWB.html)
   * [`dailyWB_SSURGO`](http://ncss-tech.github.io/sharpshootR/reference/dailyWB_SSURGO.html)
   * [`CDECquery`](http://ncss-tech.github.io/sharpshootR/reference/CDECquery.html)
   * [`CDECsnowQuery`](http://ncss-tech.github.io/sharpshootR/reference/CDECsnowQuery.html)
   * [`FFD`](http://ncss-tech.github.io/sharpshootR/reference/FFD.html)
   * [`FFDplot`](http://ncss-tech.github.io/sharpshootR/reference/FFD.html)
   * [`PCP_plot`](http://ncss-tech.github.io/sharpshootR/reference/PCP_plot.html)
   * [`waterDayYear`](http://ncss-tech.github.io/sharpshootR/reference/waterDayYear.html)


### Spatial Data
   * [`constantDensitySampling`](http://ncss-tech.github.io/sharpshootR/reference/constantDensitySampling.html)
   * [`generateLineHash`](http://ncss-tech.github.io/sharpshootR/reference/generateLineHash.html)
   * [`polygonAdjacency`](http://ncss-tech.github.io/sharpshootR/reference/polygonAdjacency.html)
   * [`PLSS2LL`](http://ncss-tech.github.io/sharpshootR/reference/PLSS2LL.html)
   * [`LL2PLSS`](http://ncss-tech.github.io/sharpshootR/reference/LL2PLSS.html)
   * [`sample.by.poly`](http://ncss-tech.github.io/sharpshootR/reference/sample.by.poly.html)
   * [`samplingStability`](http://ncss-tech.github.io/sharpshootR/reference/samplingStability.html)
   * [`sampleRasterStackByMU`](http://ncss-tech.github.io/sharpshootR/reference/sampleRasterStackByMU.html)


### Utility
   * [`component.adj.matrix`](http://ncss-tech.github.io/sharpshootR/reference/component.adj.matrix.html)
   * [`dist.along.grad`](http://ncss-tech.github.io/sharpshootR/reference/dist.along.grad.html)


### Misc.
   * [`percentileDemo`](http://ncss-tech.github.io/sharpshootR/reference/percentileDemo.html)
   * [`multinominal2logical`](http://ncss-tech.github.io/sharpshootR/reference/multinominal2logical.html)
   * [`site_photos_kml`](http://ncss-tech.github.io/sharpshootR/reference/site_photos_kml.html)


## Related Packages
 * [`aqp`](https://github.com/ncss-tech/aqp)
 * [`soilDB`](https://github.com/ncss-tech/soilDB)
 


## Related Presentations / Posters
  * [Numerical Classification of Soil Profiles (2023 NCSS Meetings)](https://ncss-tech.github.io/AQP/presentations/2023-NCSS-NCSP-poster.pdf)

